### 2015-02-26 appendices.tex
adding data files

\subsection{R CODE - QUALITY} 
\scriptsize{
\begin{lstlisting}[language=R]
# Load the Quality data.
setAs("character","myDate", function(from) as.Date(from, format="%m/%d/%Y") )
setClass('myDate')

quality_data <- read.csv('quality_data_clean.csv', 
        colClasses=c('factor','myDate','myDate','numeric','numeric',
        'numeric','numeric','numeric','numeric','numeric') )
str(quality_data)
head(quality_data)
summary(quality_data)

# Get data prior to 2013
old_quality_data = quality_data[quality_data$MONTH_DT <= as.Date('2013-12-31') ,]
str(old_quality_data)
pairs(old_quality_data[,c('TOTAL_TIX','EST_DEV_RES_HRS')] )

# Separate out large (>1000 hours) and small projects
large_quality_data = old_quality_data[old_quality_data$EST_DEV_RES_HRS >= 1000,]
str(large_quality_data)
largefit <- lm(TOTAL_TIX ~ EST_DEV_RES_HRS + DFTS_CNT_SIT + DFTS_CNT_UAT , 
        data=large_quality_data)
summary(largefit)
largefit_sigma = summary(largefit)$sigma
pairs(large_quality_data[,c('EST_DEV_RES_HRS','DFTS_CNT_SIT',
        'DFTS_CNT_UAT','TOTAL_TIX')])

small_quality_data = 
        old_quality_data[old_quality_data$EST_DEV_RES_HRS < 1000 
            && old_quality_data$APP != 'App 86' ,]
str(small_quality_data)
smallfit <- lm(TOTAL_TIX ~ EST_DEV_RES_HRS + DFTS_CNT_SIT + DFTS_CNT_UAT , 
        data=small_quality_data)
summary(smallfit)
smallfit_sigma = summary(smallfit)$sigma
pairs(small_quality_data[,c('EST_DEV_RES_HRS','DFTS_CNT_SIT',
        'DFTS_CNT_UAT','TOTAL_TIX')])

# predict new data  
new_large_quality_data = 
        quality_data[quality_data$MONTH_DT > as.Date('2013-12-31') 
            & quality_data$MONTH_DT < as.Date('2014-12-31') 
            & quality_data$EST_DEV_RES_HRS >= 1000,]
new_small_quality_data = 
        quality_data[quality_data$MONTH_DT > as.Date('2013-12-31') 
        & quality_data$MONTH_DT < as.Date('2014-12-31') 
        & quality_data$EST_DEV_RES_HRS < 1000,]
new_large_quality_data$PREDICTION = 
        predict(largefit, newdata=new_large_quality_data)
new_large_quality_data$SCORE = 
        (new_large_quality_data$PREDICTION - new_large_quality_data$TOTAL_TIX)
        / (6 * summary(largefit)$sigma)
new_large_quality_data[,c('APP','MONTH_DT','TOTAL_TIX','PREDICTION', 'SCORE')]

new_small_quality_data$PREDICTION = predict(smallfit, newdata=new_small_quality_data)
new_small_quality_data$SCORE = 
        (new_small_quality_data$PREDICTION - new_small_quality_data$TOTAL_TIX)
        / (6 * summary(smallfit)$sigma)
new_small_quality_data[,c('APP','MONTH_DT','TOTAL_TIX','PREDICTION', 'SCORE')]

#Combine new data  
new_quality_data = rbind(new_large_quality_data, new_small_quality_data)
str(new_quality_data)
summary(new_quality_data)

aggregate(SCORE ~ MONTH_DT, new_quality_data, mean)

# TODO include
# numerical summary stats, graphical summaries,
# dist of variables(hist used for guidance), associations among variables
\end{lstlisting}}

>>>>

\subsection{R CODE - QUALITY}

### 2015-02-26 paper_40_mpi.tex
adding data files

    Software development organizations struggle to measure overall performance.  
    The Master Performance Indicator (MPI) is an algorithm to provide a single 
    number score to measure the performance of a software development organization. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  MPI focuses on the following 
    elements of a software development organization: \textit{quality}, 
    \textit{availability}, \textit{satisfaction}, \textit{schedule},
    and \textit{requirements}. A separate MPI
    score is calculated for each element and 
    then aggregated together to form an overall 
    MPI score.  A new MPI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    \textbf{MPI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements}.  MPI is made to be easily 
    expandable to other elements if desired.

@@

            \paragraph{QUALITY FORMULA}
                The first step in creating a score for the quality
                element is analysis of the historical data.  The historical
                data is all quality data collected before  a given point
                in time.  Some common historical cutoffs are the current date
                or the end of the previous fiscal year.  Then a mathematical
                model to predict PROD Defects will be produced.  In statistical
                terms, the response is \textit{PROD Defects} and the predictors
                are: \textit{UAT Defects}, \textit{SIT Defects}, 
                \textit{Testing Effort}, and \textit{Development Effort}.  
                Some of the following strategies will be employed to find 
                a reasonable model.
                \begin{itemize}
                    \item Removal of outliers and/or influential points
                    \item Linear Regression
                    \item Stepwise Regression
                    \item Ridge Regression for suspected multicolinearity
                \end{itemize}

>>>>

    Software development organizations struggle to measure overall performance.  
    The Master Performance Indicator (MPI) is an algorithm to provide a single 
    number score to measure the performance of a software development organization. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  MPI is a collection of the following 5 
    elements, which are actually KRIs,
    for a software development organization.
    \textbf{
    \begin{enumerate}
        \item Quality
        \item Availability
        \item Satisfaction
        \item Schedule
        \item Requirements
    \end{enumerate}
    }
    A separate MPI
    score is calculated for each element and 
    then aggregated together to form an overall 
    MPI score.  A new MPI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    \textbf{MPI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements}.  MPI is made to be easily 
    expandable to other elements if desired.

@@

            \paragraph{QUALITY FORMULA}
                The first step in creating a score for the quality
                element is analysis of the historical data to create
                a baseline function.  The historical
                data is all quality data collected before  a given point
                in time.  Some common historical cutoffs are the current date
                or the end of the previous fiscal year.  Then a mathematical
                model, called the \textit{baseline quality function},
                to predict PROD Defects will be produced.  In statistical
                terms, the response is \textit{PROD Defects} and the predictors
                are: \textit{UAT Defects}, \textit{SIT Defects}, 
                \textit{Testing Effort}, and \textit{Development Effort}.  
                Some of the following strategies will be employed to find 
                a reasonable model.
                \begin{itemize}
                    \item Removal of outliers and/or influential points
                    \item Linear Regression
                    \item Stepwise Regression
                    \item Ridge Regression for suspected multicolinearity
                \end{itemize}

### 2015-02-26 paper_70_case-study.tex
working on the end of chapter 4
chapter 3 work
mostly done with chapter 3
adding data files

Data has been collected from the software development processes of
an SDO within a large financial institution.
The data collection was from 2008 to present. This section will provide the analysis performed and the MPI scores of that data. The data is incomplete but that is realistic of most oganizations.  Currently, the data
consists of availability, quality, and schedule.  Satisfaction and Requirements are being obtained. An example of the initial analysis is included in \cref{app:case}.

\subsection{WITHOUT HISTORICAL DATA}

An MPI calculation with default values.

\subsection{WITH HISTORICAL DATA}

How to create better formulas with historical data.

>>>>

Data has been collected from the software development processes of
an SDO within a large financial institution.
The data collection was from 2007 to January 2015. As would be expected
in any organization, not all 5 elements have data for the entire duration.
MPI can still work because the calculations will only include
the available elements.  This section will provide the analysis performed and the MPI scores of that data.  An example of the initial analysis is included in \cref{app:case}.

\subsection{WITH HISTORICAL DATA}
    This first case will demonstrate how to calculate the MPI for an
    organization when historical data is present.  
    \subsubsection{QUALITY}
        Luckily, the data for quality goes from October 2007 to January 2015
        and contains 985 observations.
        This is important because historical data can be used to create the
        baseline quality function.  All quality for the years 2007 through 2013
        will be used as historical data for the purposes of creating
        the baseline quality function.  
    \subsubsection{AVAILABILITY}
    \subsubsection{SATISFACTION}
    \subsubsection{SCHEDULE}
    \subsubsection{REQUIREMENTS}
    \subsubsection{OVERALL}
        All of the months do not include the same elements.

An MPI calculation analyzing historical performance.

%%\subsection{WITHOUT HISTORICAL DATA}

%%An MPI calculation with default values for quality, schedule and requirements.
